Drought-sensitive trees survive on deep water access in a tropical forest community

### 2020-08-05 manuscript.rmd
minor edit

## Study Site Description
\
We conducted this study at the seasonally dry tropical forest on Barro Colorado Island (BCI), Panama, given its extensive characterization in terms of long-term forest demography, plant functional ecology, hydrology, and water sourcing depth water isotopes on tree species and soil from an independent isotopic tracer study on trees’ water-sourcing depths [@Meinzer:1999]. The 1,560ha island was formed after the river Chagres was dammed in 1914 that created Gatun Lake, the main channel of the Panama Canal. Rainfall at BCI is seasonal with a mean annual rainfall of 2687 mm (± 515 SD over 1983-2017) and a four-month long dry season from mid-December through mid-April (≤ 100 mm rain/month). The entire island is forested and classified as a tropical moist forest. Although percentage of canopy species that are at least partly deciduous during the dry season is 28%, the maximum percentage of deciduous individuals in the canopy is only 6.3%, and the percentage of crown area that is deciduous is estimated at 9.7% [@Condit:2000]. Long-term hydrological monitoring at BCI began in 1972, while demographical monitoring began with the 50ha ForestGEO plot establishment in 1981-82 [@Condit.1998uq; @Hubbell:1999; @Anderson-Teixeira:2014].

>>>>

## Study Site Description
\
We conducted this study at the seasonally dry tropical forest on Barro Colorado Island (BCI), Panama, given its extensive characterization in terms of long-term forest demography, plant functional ecology, hydrology, and water sourcing depth water isotopes on tree species and soil from an independent isotopic tracer study on trees’ water-sourcing depths [@Meinzer:1999]. The 1,560ha island was formed after the river Chagres was dammed in 1914 that created Gatun Lake, the main channel of the Panama Canal. Rainfall at BCI is seasonal with a mean annual rainfall of 2687 mm (± 515 SD; 1983-2017) and a four-month long dry season from mid-December through mid-April (≤ 100 mm rain/month). The entire island is forested and classified as a tropical moist forest. Although percentage of canopy species that are at least partly deciduous during the dry season is 28%, the maximum percentage of deciduous individuals in the canopy is only 6.3%, and the percentage of crown area that is deciduous is estimated at 9.7% [@Condit:2000]. Long-term hydrological monitoring at BCI began in 1972, while demographical monitoring began with the 50ha ForestGEO plot establishment in 1981-82 [@Condit.1998uq; @Hubbell:1999; @Anderson-Teixeira:2014].
